Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
bis
MFCCs should not be between dollars

Our results on the development dataset are reported in Table \ref{table:dcase2016}, in comparison with a baseline of $MFCCs$ coefficients and a generative classifier, namely Gaussian mixture models with $16$ Gaussians per model. The baseline relies on a late integration scheme, wherein the reduction function $\rho$ is a product of likelihoods.
The average accuracy across classes is brought from $70.8\%$ to $79.4\%$.
The results on the evaluation dataset are awaiting publication by the DCASE organizing committee, and will be disclosed in August 2016.

\begin{table}
\begin{center}
\caption{Class-wise accuracies on the DCASE 2016 dataset for the baseline and proposed algorithms.}
\begin{tabular}{lcc}
Features & MFCCs & log-scattering \\
Classifier  & GMMs    & linear SVMs \\
Temporal integration & late (product rule) & late (majority voting) \\
\midrule
beach & $74.6 \pm 18.9$ & $83.5 \pm \phantom{0}7.1$ \\
bus & $58.2 \pm 18.3$ & $88.8 \pm 11.4$ \\
caf\'{e} / restaurant & $85.1 \pm 10.8$ & $64.5 \pm \phantom{0}8.3$ \\
car & $69.1 \pm 20.8$ & $94.9 \pm \phantom{0}6.1$ \\
city center & $89.6 \pm \phantom{0}9.2$ & $91.7 \pm \phantom{0}9.4$ \\
forest path & $72.4 \pm 23.8$ & $93.8 \pm \phantom{0}7.8$ \\
grocery store & $74.1 \pm 13.7$ & $90.9 \pm \phantom{0}6.9$ \\
home & $78.1 \pm 17.7$ & $56.2 \pm 23.9$ \\
library & $65.1 \pm 23.3$ & $82.0 \pm 13.0$ \\
metro station & $85.2 \pm 15.6$ & $96.0 \pm \phantom{0}2.3$ \\
office & $90.8 \pm 16.0$ & $87.5 \pm 21.7$ \\
park & $25.6 \pm 11.0$ & $75.4 \pm \phantom{0}7.4$ \\
residential area & $75.1 \pm 19.4$ & $44.2 \pm 15.0$ \\
train & $34.1 \pm \phantom{0}7.2$ & $58.3 \pm 10.0$ \\
tram & $85.4 \pm 13.9$ & $83.7 \pm 12.2$ \\
\bottomrule
Average & $70.8 \pm \phantom{0}2.6$ & $79.4 \pm \phantom{0}3.0$
\end{tabular}
\end{center}
\label{table:dcase2016}
\end{table}

>>>>

Our results on the development dataset are reported in Table \ref{table:dcase2016}, in comparison with a baseline of MFCCs coefficients and a generative classifier, namely Gaussian mixture models with $16$ Gaussians per model. The baseline relies on a late integration scheme, wherein the reduction function $\rho$ is a product of likelihoods.
The average accuracy across classes is brought from $70.8\%$ to $79.4\%$.
The results on the evaluation dataset are awaiting publication by the DCASE organizing committee, and will be disclosed in August 2016.

\begin{table}
\begin{center}
\caption{Class-wise accuracies on the DCASE 2016 dataset for the baseline algorithm (left) and proposed algorithm (right).}
\begin{tabular}{lcc}
Features & MFCCs & log-scattering \\
Classifier  & GMMs    & linear SVMs \\
Temporal integration & late (product rule) & late (majority voting) \\
\midrule
beach & $74.6 \pm 18.9$ & $83.5 \pm \phantom{0}7.1$ \\
bus & $58.2 \pm 18.3$ & $88.8 \pm 11.4$ \\
caf\'{e} / restaurant & $85.1 \pm 10.8$ & $64.5 \pm \phantom{0}8.3$ \\
car & $69.1 \pm 20.8$ & $94.9 \pm \phantom{0}6.1$ \\
city center & $89.6 \pm \phantom{0}9.2$ & $91.7 \pm \phantom{0}9.4$ \\
forest path & $72.4 \pm 23.8$ & $93.8 \pm \phantom{0}7.8$ \\
grocery store & $74.1 \pm 13.7$ & $90.9 \pm \phantom{0}6.9$ \\
home & $78.1 \pm 17.7$ & $56.2 \pm 23.9$ \\
library & $65.1 \pm 23.3$ & $82.0 \pm 13.0$ \\
metro station & $85.2 \pm 15.6$ & $96.0 \pm \phantom{0}2.3$ \\
office & $90.8 \pm 16.0$ & $87.5 \pm 21.7$ \\
park & $25.6 \pm 11.0$ & $75.4 \pm \phantom{0}7.4$ \\
residential area & $75.1 \pm 19.4$ & $44.2 \pm 15.0$ \\
train & $34.1 \pm \phantom{0}7.2$ & $58.3 \pm 10.0$ \\
tram & $85.4 \pm 13.9$ & $83.7 \pm 12.2$ \\
\bottomrule
Average & $70.8 \pm \phantom{0}2.6$ & $79.4 \pm \phantom{0}3.0$
\end{tabular}
\end{center}
\label{table:dcase2016}
\end{table}
